\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-21 paper.qmd
Add intro for methodology section

In this paper, we introduce a novel approach, which is designed to determine which method, and which parameter choice provide the most useful representation of high dimensional data. Our approach involves dividing the data set into two subsets: a training set, which serves to construct the low-dimensional manifold, and a test set, utilized to generate predictive values and residuals. For the implementation of our approach, a 2D embedding data set serves as the initiation point for the subsequent analysis and visualization. The output

write about the S-curve as well.

Our algorithm comprises two main phases: (1) generate the model in the 2D space, and (2) generate the model in the high-D space. These two phases are described in details in this section.

>>>>

In this paper, we present a novel method that aims to determine the most effective way to represent high-D data by selecting the best method and hyperparameter choice. Our approach involves dividing the data set into two parts: a training set to construct the model and a test set to generate predictive values and residuals. To implement our approach, we first use a 2D embedding data set as the initial point. The output of our algorithm is a tour that displays the model and original data in the high-dimensional space. A flow chart of the proposed algorithm is shown in @fig-meth. Our algorithm comprises two main phases: (1) generate the model in the 2D space, and (2) generate the model in the high-D space. These two phases are described in detail in this section using UMAP 2D embedding of the S-curve data set, which has seven dimensions, including four noise dimensions.

### 2024-01-21 paper.tex
Add intro for methodology section

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

In this paper, we introduce a novel approach, which is designed to
determine which method, and which parameter choice provide the most
useful representation of high dimensional data. Our approach involves
dividing the data set into two subsets: a training set, which serves to
construct the low-dimensional manifold, and a test set, utilized to
generate predictive values and residuals. For the implementation of our
approach, a 2D embedding data set serves as the initiation point for the
subsequent analysis and visualization. The output

write about the S-curve as well.

Our algorithm comprises two main phases: (1) generate the model in the
2D space, and (2) generate the model in the high-D space. These two
phases are described in details in this section.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, frame hidden, breakable, sharp corners, enhanced]}{\end{tcolorbox}}\fi

@@

In this paper, we present a novel method that aims to determine the most
effective way to represent high-D data by selecting the best method and
hyperparameter choice. Our approach involves dividing the data set into
two parts: a training set to construct the model and a test set to
generate predictive values and residuals. To implement our approach, we
first use a 2D embedding data set as the initial point. The output of
our algorithm is a tour that displays the model and original data in the
high-dimensional space. A flow chart of the proposed algorithm is shown
in Figure~\ref{fig-meth}. Our algorithm comprises two main phases: (1)
generate the model in the 2D space, and (2) generate the model in the
high-D space. These two phases are described in detail in this section
using UMAP 2D embedding of the S-curve data set, which has seven
dimensions, including four noise dimensions.
